% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\Large\bf Cory Heslip}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{10124 Inverness Main St}
 \moveleft.5\hoffset\centerline{Englewood, CO 80112}
 \moveleft.5\hoffset\centerline{(720) 989-6512}


\begin{resume}
 
\section{PROFILE}  Experienced software engineer with a unique background in both computer
		and life sciences. A self-starter with a demonstrated ability to quickly learn, adapt and utilize a variety of languages and technologies to solve problems and create new user experiences.
 
\section{TECHNICAL \\ SKILLS}
        {\sl Languages:} Expert in Java and Python, proficient in JavaScript and Objective-C, and well versed C++ and PHP. \\
        {\sl Web Technologies:} JavaScript, HTML, CSS, LESS, jQuery, JSON, REST, AJAX \\
        {\sl Databases:} PostgreSQL, MySQL, SQLite, PHP, HTML, CSS, jQuery, JSON, REST, AJAX, Git, Perforce \\
        {\sl Source Control:} Git, Perforce
		{\sl Software:} Eclipse, Netbeans, Xcode, PyCharm, Chrome \\
        {\sl Operating Systems:} Mac OS, Linux, Windows, iOS, Android

\section{PROJECTS}
		{\sl Specimen Suitability App:}	iOS and Android app that aids the organ and tissue donor
		community in determining the testing suitability of blood specimens. (Obj-C, Java). \\ \\
		{\sl Specimen Archiver:} Web based application to simplify tracking and
		storing laboratory specimens (PHP, MySQL). \\ \\ 
		{\sl Open Garage:} Website for a social networking startup that aims to connect people with others in
		order to learn a new hobby or skill (Python, Django framework).\\ \\
		{\sl See more on GitHub:} https://github.com/cheslip/
 
\section{EXPERIENCE}
        {\sl Software Engineer (mid-level)} \hfill Auguest 2013 - present \\
        {\bf Time Warner Cable (contractor)}, Native Client Navigation, Broomfield, CO
        \begin{itemize} \itemsep -2pt
        \item Made rich user experience possible on legacy set top boxes by improving efficiency of JPEG image loading.
        \item Implemented remote commands for digital video recorder functionality to support mobile initiative.
        \item Created a system profiling tool using Python and JavaScript (AngularJS) to discover problem areas in codebase.
        \item Increased performance of digital video recording for next generation navigation platform in multiple areas by using profiling tool.
        \end{itemize}
    % -----------------------------------------------------------------------------------------
        {\sl Software Engineering Intern} \hfill June 2013 - August 2013 \\
        {\bf Time Warner Cable}, Native Client Navigation, Broomfield, CO
        \begin{itemize} \itemsep -2pt
        \item Designed and implemented in Java a replacement for a legacy configuration management system for set top boxes.
        \item Utilized JUnit to bring test code coverage of configuration management to 90\%
        \end{itemize}
    % -----------------------------------------------------------------------------------------    
		{\sl Laboratory Technologist / Mobile App Developer} \hfill March 2011 - present \\
        {\bf VRL Laboratories}, Infectious Disease Department, Centennial, CO 
        \begin{itemize}  \itemsep -2pt %reduce space between items
		\item Created the VRL Specimen Suitability App for iOS and Android. 
			This app assists clients in determining specimen suitability.
        \item	Improved night shift logistics by creating a Microsoft Outlook script
			to track incoming specimen shipments.
		\item	Perform ELISA and nucleic acid testing of 40 blood specimens per night on average.
    	\end{itemize}
    % -----------------------------------------------------------------------------------------
        {\sl Web Application Developer / Co-Founder} \hfill            July 2012 - present \\
        {\bf Open Garage},		currently in development
        \begin{itemize}  \itemsep -2pt %reduce space between items
		\item Utilized the Django framework and many different web technologies to build a unique new social network from the ground up.
		\item Created new features by using Python, JavaScript, JQuery and by customizing existing open source projects
		\item Designed a simple and pleasing user interface using CSS and JavaScript.
		\item Deployed the current state of the website to testers in order to gain feedback for improvements.
     	\end{itemize} 
     	
\section{EDUCATION} 
		{\sl Master of Science,} Computer Software Engineering \\
		Colorado Technical University, Denver, CO, expected 2014 \\
		{\sl \indent Current GPA: } 3.6
		
		{\sl Bachelor of Arts,} Biology and Chemistry \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                University of Colorado at Colorado Springs, Colorado Springs, CO, 
                May 2010 \\ 
		{\sl Associations:} Beta Beta Beta Biological Honor Society
        

\end{resume}
\end{document}




